Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring

### 2014-05-30 evaluation.tex
Multi-run coverage results.

>>>>

\subsection{Multiple-Run Coverage}

% Multi-run coverage with unrestricted dropping
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/data_multirun_coverage.pdf}
    \vspace{-0.2in}
    \caption{Coverage over multiple runs for BC at 20\% overhead.}
    \label{fig:evaluation.multirun}
    \vspace{-0.1in}
  \end{center}
\end{figure}

One possible application of partial monitoring with low overheads is to enable
cooperative debugging. The idea with cooperative debugging is to enable partial
monitoring with very low overheads across a large number of users or runs. By
varying the pattern of partial monitoring done on each run, the goal is to
achieve high or total coverage across all runs. Varying the monitoring that is
done for different runs can be achieved by introducing some randomness into the
dropping decision. Figure~\ref{fig:evaluation.multirun} shows the total
coverage achieved over multiple runs for array bounds check running with a 20\%
overhead budget and an unrestricted dropping policy. Here, when events are
dropped probabilistically with the probability scaled proportionally to slack.
That is, when slack is high, the probability of dropping is low and the
probability increases as we run out of slack. We see that the coverage achieved
quickly asymptotes for an unrestricted dropping policy. This is due to the fact
that since there are multiple dependent monitoring operations that must be done
in order for a final check to be successful, a small amount of randomness at
each event quickly compounds to reduce the probability of certain checks to
near zero. Instead, source dropping is much better suited for achieve high
coverage over multiple runs.
